### 2004-07-13 Documentation/Manual.tex
extended the \GLB command to handle a leading '@' (this is meta character for makeindex and thus has to be escaped by '"'). Added a label for section 7.2
added section about globes put in the fdl part on page two, made the sections of fdl disappear from toc added multiple index support changed the \GLB and \GLBNS commands such, that they prepend 'glb' in the text and add their argument to the api index. makeindex has not be called four times: 	makeindex norm.idx 	makeindex api.idx 	makeindex aedl.idx 	makeindex constants.idx
Adding entries now works with \index{index_name}{index_entry}, e.g.
\

\usepackage{verbatim}
\usepackage{cite}
\usepackage[dvips]{color}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{a4wide}
\usepackage{fancyheadings}
\usepackage[footnotesize,bf]{caption}
\usepackage{makeidx}
\usepackage{ae,aecompl} % only for Type 1 fonts for readable pdf convert

@@

% Index: use "makeindex Manual" to create .ind file
\makeindex

@@

% Set as GLoBES command and add to index:
% Always use GLB when mentioning a command in text!
\newcommand{\GLB}[1]{{\tt #1}\index{{\tt #1}}}
% Always use GLBNS when adding a command to the index without showing it!
\newcommand{\GLBNS}[1]{\index{{\tt #1}}}
\newcommand{\gq}[1]{\begin{quote} {\tt #1} \end{quote}}
\newcommand{\go}[1]{$\rightarrow$ Output: \begin{quote} {\sf #1} \end{quote}}

@@

\clearpage
\thispagestyle{empty}

@@

\printindex

>>>>

\usepackage{verbatim}
\usepackage{cite}
\usepackage[dvips]{color}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{a4wide}
\usepackage{fancyheadings}
\usepackage[footnotesize,bf]{caption}
\usepackage{makeidx}
%Preparations for multiple indices
\usepackage{multind}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{ae,aecompl} % only for Type 1 fonts for readable pdf convert

@@

% Index: use "makeindex Manual" to create .ind file
%\makeindex

\makeindex{norm}
\makeindex{constants}
\makeindex{api}
\makeindex{aedl}

@@

% Set as GLoBES command and add to index:
% Always use GLB when mentioning a command in text!
\newcommand{\GLB}[1]{{\tt glb#1}\index{api}{#1@{\tt #1}}}
% Always use GLBNS when adding a command to the index without showing it!
\newcommand{\GLBNS}[1]{\index{api}{#1@{\tt #1}}}

% Set as GLoBES command and add to index:
% Always use GLB when mentioning a command in text!
\newcommand{\GLBC}[1]{{\tt #1}\index{constants}{{\tt  #1}}}
% Always use GLBNS when adding a command to the index without showing it!
\newcommand{\GLBNSC}[1]{\index{constants}{{\tt #1}}}
\newcommand{\gq}[1]{\begin{quote} {\tt #1} \end{quote}}
\newcommand{\go}[1]{$\rightarrow$ Output: \begin{quote} {\sf #1} \end{quote}}

@@

\clearpage
\thispagestyle{empty}
\bigskip
\begin{quote}
    Copyright \copyright  2004  The GLoBES Team.
    Permission is granted to copy, distribute and/or modify this document
    under the terms of the GNU Free Documentation License, Version 1.2
    or any later version published by the Free Software Foundation;
    with no Invariant Sections, no Front-Cover Texts, and no Back-Cover Texts.
    A copy of the license is included in the section entitled "GNU
    Free Documentation License".
\end{quote}
\bigskip

@@

\printindex{api}{API functions}
\printindex{constants}{API constants \& macros}
\printindex{aedl}{AEDL reference}
\printindex{norm}{Index}

### 2004-07-13 Documentation/fdl.tex
added section about globes put in the fdl part on page two, made the sections of fdl disappear from toc added multiple index support changed the \GLB and \GLBNS commands such, that they prepend 'glb' in the text and add their argument to the api index. makeindex has not be called four times: 	makeindex norm.idx 	makeindex api.idx 	makeindex aedl.idx 	makeindex constants.idx
Adding entries now works with \index{index_name}{index_entry}, e.g.
\index{norm}{Blau} adds 'Blau' to the usual index.

\begin{center}
{\Large\bf 1. APPLICABILITY AND DEFINITIONS}
\addcontentsline{toc}{section}{1. APPLICABILITY AND DEFINITIONS}
\end{center}

@@

\begin{center}
{\Large\bf 2. VERBATIM COPYING}
\addcontentsline{toc}{section}{2. VERBATIM COPYING}
\end{center}

@@

\begin{center}
{\Large\bf 3. COPYING IN QUANTITY}
\addcontentsline{toc}{section}{3. COPYING IN QUANTITY}
\end{center}

@@

\begin{center}
{\Large\bf 4. MODIFICATIONS}
\addcontentsline{toc}{section}{4. MODIFICATIONS}
\end{center}

@@

\begin{center}
{\Large\bf 5. COMBINING DOCUMENTS}
\addcontentsline{toc}{section}{5. COMBINING DOCUMENTS}
\end{center}

@@

\begin{center}
{\Large\bf 6. COLLECTIONS OF DOCUMENTS}
\addcontentsline{toc}{section}{6. COLLECTIONS OF DOCUMENTS}
\end{center}

@@

\begin{center}
{\Large\bf 7. AGGREGATION WITH INDEPENDENT WORKS}
\addcontentsline{toc}{section}{7. AGGREGATION WITH INDEPENDENT WORKS}
\end{center}

@@

\begin{center}
{\Large\bf 8. TRANSLATION}
\addcontentsline{toc}{section}{8. TRANSLATION}
\end{center}

@@

\begin{center}
{\Large\bf 9. TERMINATION}
\addcontentsline{toc}{section}{9. TERMINATION}
\end{center}

@@

\begin{center}
{\Large\bf 10. FUTURE REVISIONS OF THIS LICENSE}
\addcontentsline{toc}{section}{10. FUTURE REVISIONS OF THIS LICENSE}
\end{center}

@@

\begin{center}
{\Large\bf ADDENDUM: How to use this License for your documents}
\addcontentsline{toc}{section}{ADDENDUM: How to use this License for your documents}
\end{center}

To use this License in a document you have written, include a copy of
the License in the document and put the following copyright and
license notices just after the title page:

\bigskip
\begin{quote}
    Copyright \copyright  YEAR  YOUR NAME.
    Permission is granted to copy, distribute and/or modify this document
    under the terms of the GNU Free Documentation License, Version 1.2
    or any later version published by the Free Software Foundation;
    with no Invariant Sections, no Front-Cover Texts, and no Back-Cover Texts.
    A copy of the license is included in the section entitled "GNU
    Free Documentation License".
\end{quote}
\bigskip

If you have Invariant Sections, Front-Cover Texts and Back-Cover Texts,
replace the "with...Texts." line with this:

\bigskip
\begin{quote}
    with the Invariant Sections being LIST THEIR TITLES, with the
    Front-Cover Texts being LIST, and with the Back-Cover Texts being LIST.
\end{quote}
\bigskip

If you have Invariant Sections without Cover Texts, or some other
combination of the three, merge those two alternatives to suit the
situation.

If your document contains nontrivial examples of program code, we
recommend releasing these examples in parallel under your choice of
free software license, such as the GNU General Public License,
to permit their use in free software.

>>>>

\begin{center}
{\Large\bf 1. APPLICABILITY AND DEFINITIONS}
%\addcontentsline{toc}{section}{1. APPLICABILITY AND DEFINITIONS}
\end{center}

@@

\begin{center}
{\Large\bf 2. VERBATIM COPYING}
%\addcontentsline{toc}{section}{2. VERBATIM COPYING}
\end{center}

@@

\begin{center}
{\Large\bf 3. COPYING IN QUANTITY}
%\addcontentsline{toc}{section}{3. COPYING IN QUANTITY}
\end{center}

@@

\begin{center}
{\Large\bf 4. MODIFICATIONS}
%\addcontentsline{toc}{section}{4. MODIFICATIONS}
\end{center}

@@

\begin{center}
{\Large\bf 5. COMBINING DOCUMENTS}
%\addcontentsline{toc}{section}{5. COMBINING DOCUMENTS}
\end{center}

@@

\begin{center}
{\Large\bf 6. COLLECTIONS OF DOCUMENTS}
%\addcontentsline{toc}{section}{6. COLLECTIONS OF DOCUMENTS}
\end{center}

@@

\begin{center}
{\Large\bf 7. AGGREGATION WITH INDEPENDENT WORKS}
%\addcontentsline{toc}{section}{7. AGGREGATION WITH INDEPENDENT WORKS}
\end{center}

@@

\begin{center}
{\Large\bf 8. TRANSLATION}
%\addcontentsline{toc}{section}{8. TRANSLATION}
\end{center}

@@

\begin{center}
{\Large\bf 9. TERMINATION}
%\addcontentsline{toc}{section}{9. TERMINATION}
\end{center}

@@

\begin{center}
{\Large\bf 10. FUTURE REVISIONS OF THIS LICENSE}
%\addcontentsline{toc}{section}{10. FUTURE REVISIONS OF THIS LICENSE}
\end{center}

@@

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "Manual"
%%% End:
